---
title: "ryx"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ryx}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ryx)
```

# Introduction

This package contain the following functions ryx, print, plot, and summary. The ryx function will create a table of correlation given a y variable and a vector x of variables in the data frame. Since the return value is of class "ryx", the print, plot, and summary functions included will work appropriately for the returned value.

# Function RYX

Create a correlation table with this function of class "ryx"

```{r eval=FALSE}
Library(MASS)
x <- ryx(Boston, y = "medv", x = c("age","dis","lstat"))
```

# Function Print

This function will print the correlation table without rownames

```{r eval=FALSE}
print(x) #x is of class "ryx"
```

# Function Summary

This function will show a customized summary of the data. Click on the summary details for more in-depth info

```{r eval=FALSE}
summary(x) #x is of class "ryx"
```

# Function Plot

This function will print a ggplot of variables v. absolute values of correlation

```{r eval=FALSE}
plot(x) #x is of class "ryx"
```
